An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-31 EconGrowth2.Rnw
Deleted much old text dealing with no-longer-used graphs. Replaced by faceted graphs for CES resampling parameters.

Coefficients for each resampled CES model (without energy)
are shown in 
Figures~\ref{fig:CES_lambda_gamma_Scatter_Graph} and
\ref{fig:CES_sigma_1_delta_1_Scatter_Graph}. 
Note that the bottom of the vertical axis represents $\sigma = 0$.
The top of the vertical axis represents $\sigma = \infty$.
The crosshair on each graph shows the location 
of the fit to historical data. 
Dots are colored by whether or not the fitting routine
reports model convergence.

<<CES_lambda_gamma_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="none")
@

<<CES_sigma_1_delta_1_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="none")
@

Coefficients for each resampled CES model (with energy)
are shown in 
Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_ekl}. 
Note that each nesting of the factors of production
is included in the graphs.

<<CESq_lambda_gamma_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="Q", nest="(kl)e")
@

<<CESq_sigma_1_delta_1_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(kl)e")
@

<<CESq_sigma_delta_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(kl)e")
@

<<CESq_lambda_gamma_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="Q", nest="(le)k")
@

<<CESq_sigma_1_delta_1_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(le)k")
@

<<CESq_sigma_delta_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(le)k")
@

<<CESq_lambda_gamma_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
cesResamplePlotLambdaGamma(energyType="Q", nest="(ek)l")
@

<<CESq_sigma_1_delta_1_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(ek)l")
@

<<CESq_sigma_delta_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(ek)l")
@

@@

**** Fix $x$-axis on Figures~\ref{fig:CESq_Sigma_Sigma_1_kle}--\ref{fig:CESq_Sigma_Sigma_1_ekl}.
Or, consider a better way to show resampled $\sigma$ and $\sigma_1$ values. ****

Figure~\ref{fig:CESq_Sigma_Sigma_1_kle} shows 
$\sigma$ and $\sigma_1$ values from the CES model with ($kl$)$e$ nesting.

<<CESq_Sigma_Sigma_1_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($kl$)$e$ nesting.">>=
cesResamplePlotSigmaSigma_1(energyType="Q", nest="(kl)e")
@

Figure~\ref{fig:CESq_Sigma_Sigma_1_lek} shows 
$\sigma$ and $\sigma_1$ values from the CES model with ($le$)$k$ nesting.

<<CESq_Sigma_Sigma_1_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($le$)$k$ nesting.">>=
cesResamplePlotSigmaSigma_1(energyType="Q", nest="(le)k")
@

Figure~\ref{fig:CESq_Sigma_Sigma_1_ekl} shows 
$\sigma$ and $\sigma_1$ values from the CES model with ($ek$)$l$ nesting.

<<CESq_Sigma_Sigma_1_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($ek$)$l$ nesting.">>=
cesResamplePlotSigmaSigma_1(energyType="Q", nest="(ek)l")
@

>>>>

Coefficients for each resampled CES model for all countries and all nests
are shown in 
Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_sigma_delta_graph}. 
The crosshair on each graph shows the location 
of the fit to historical data. 
In Figures~\ref{fig:CES_sigma1_delta1_graph} and~\ref{fig:CES_sigma_delta_graph},
the bottom of the vertical axis represents $\sigma = 0$.
The top of the vertical axis represents $\sigma = \infty$.

<<CES_lambda_gamma_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
standardScatterPlot(data=cesQResampleData, mapping=aes(gamma_coef, lambda), facet_formula=countryAbbrev~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
standardScatterPlot(data=cesQResampleData, mapping=aes(delta_1, sigma_1), facet_formula=countryAbbrev~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
standardScatterPlot(data=subset(cesQResampleData, nest!="(kl)"), 
                                mapping=aes(delta, sigma), 
                                facet_formula=countryAbbrev~nest, 
                                alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@
